\bf Model Visualization Techniques for a Social Network Model

### 2017-04-12 paper.Rnw
network data intro

@@

Network visualization, also called network mapping, is a prominent subfield of network analysis. Visualizing network data is uniquely difficult because of the structure of the data itself.  Most visualizations rely on a well-defined axis inherited from the data. If data are numerical, histograms, scatterplots, or time series plots are straightforward to construct. If the data are categorical, bar charts and mosaic plots can be constructed easily. If the data are spatial, there is a well-defined space in which to view information. Network data are much less cut-and-dried.

>>>>

Network data is of frequent interest to researchers in a wide array of fields. There are techonological networks, like power grids or the internet, information networks, such as citation networks or the World Wide Web, biological networks, e.g. neural networks, and social networks, just to name a few \citep{newman}. Each of these examples have one thing in common: their data structure. There are always units of observation, which we refer to throughout as nodes, and connections of some kind between those units, which we will call edges. The networks can also vary over time, for example when new websites and hyperlinks are added on the World Wide Web, or when there are new people and relationships in a friendship network. The nodes and edges themselves also have inherent variables of interest, such as the the affiliation of authors in a coauthorship network, and the number of times two authors have collaborated.

The multiple layers, so to speak, of network data structures create unique struggles to network analysts. Some questions that researchers aim to answer can be: How does the strength of a connection between two nodes affect the overall structure of the network? Do node-level differences affect the formation or destruction of edges? Which views of the data are most informative for communicating effects and results of statistical analyses? These are, of course, just a few broad questions, and we will focus on only the latter.

@@

Network visualization, also called network mapping, is a prominent subfield of network analysis. Visualizing network data is uniquely difficult because of the structure of the data itself.  Most, if not all, data visualizations rely on a well-defined axis inherited from the data. If data are numerical, histograms, scatterplots, or time series plots are straightforward to construct. If the data are categorical, bar charts and mosaic plots are available to to the researcher. If the data are spatial, there is a well-defined region in which to view information. Network data, however, are much less cut-and-dried.
